---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

This is a work in progress investigating some of the ideas and concepts in the book, Games of Life by Karl Sigmund. The idea is to get a visual impression of some of the basic and fundamental processes in evolutionary biology. Usually, the function (like `random_drifts()`) will output a ggplot object at the end, from which you can extract all of the simulation data or fiddle with the plot to make it prettier.

## Installation

```{r, eval = FALSE}
# Install this development version from GitHub: (I don't think it will ever go on CRAN)
# install.packages("devtools")
devtools::install_github("Euphrasiologist/GOL")
```

## Dependencies

So far, the only dependencies are data.table and ggplot2. Install them as follows:

```{r, eval=FALSE}
install.packages("data.table"); install.packages("ggplot2")
library(data.table); library(ggplot2)
```

## Usage

I hope that it's all very easy to work. Adjust the parameters in the function and you're away! 

```{r example}

random_drifts(colours = 5, trials = 500, size = 300)

```

## Improvements

Hopefully at some point I will write a litte document explaining the functions and why they are interesting, but I will wait until there is a critical mass of sufficiently good functions before I do so!